\begin{center}
    \begin{longtable}{ | m{30em} | m{1.5em} | m{1.5em} | }
    \caption{Ethical Consideration Table}
    \label{tbl:ethical-table}
    \hline
    & Yes & No \ \\ \hline
    \cellcolor[HTML]{C0C0C0} Section 1: HUMANS &  & \  \\ \hline
    Does your project involve human participants? &  & x \\ \hline
    \cellcolor[HTML]{C0C0C0} Section 2: PROTECTION OF PERSONAL DATA &  & \  \\ \hline
    Does your project involve personal data collection and/or processing? & & x \\ \hline
    Does it involve the collection and/or processing of sensitive personal data (e.g. health, sexual lifestyle, ethnicity, political opinion, religious or philosophical conviction)? & & x \\ \hline
    Does it involve processing of genetic information? & & x  \\ \hline
    Does it involve tracking or observation of participants? It should be noted that this issue is not limited to surveillance or localization data. It also applies to Wan data such as IP address, MACs, cookies etc. & & x  \\ \hline
    Does your project involve further processing of previously collected personal data (secondary use)? For example Does your project involve merging existing data sets? & x &  \\ \hline
    \cellcolor[HTML]{C0C0C0} Section 3: ANIMALS & & \  \\ \hline
    Does your project involve animals? & & x  \\ \hline
    \cellcolor[HTML]{C0C0C0} Section 4: DEVELOPING COUNTRIES &  & \  \\ \hline
    Does your project involve developing countries? & & x  \\ \hline
    If your project involves low and/or lower-middle income countries, are any benefit-sharing actions planned? & & x  \\ \hline
    Could the situation in the country put the individuals taking part in the project at risk? & & x  \\ \hline
    \cellcolor[HTML]{C0C0C0} Section 5: ENVIRONMENTAL PROTECTION AND SAFETY &  & \  \\ \hline
    Does your project involve the use of elements that may cause harm to the environment, animals or plants? & & x  \\ \hline
    Does your project involve the use of elements that may cause harm to humans, including project staff? & & x  \\ \hline
    Section 6: DUAL USE &  & \  \\ \hline
    Does your project have the potential for military applications? & & x  \\ \hline
    Does your project have an exclusive civilian application focus? & & x  \\ \hline
    Will your project use or produce goods or information that will require export licenses in accordance with legislation on dual use items? & & x  \\ \hline
    Does your project affect current standards in military ethics – e.g., global ban on weapons of mass destruction, issues of proportionality, discrimination of combatants and accountability in drone and autonomous robotics developments, incendiary or laser weapons? & & x  \\ \hline
    \cellcolor[HTML]{C0C0C0} Section 7: MISUSE &  & \  \\ \hline
    Does your project have the potential for malevolent/criminal/terrorist abuse? & & x  \\ \hline
    Does your project involve information on/or the use of biological-, chemical-, nuclear/radiological-security sensitive materials and explosives, and means of their delivery? & & x  \\ \hline
    Does your project involve the development of technologies or the creation of information that could have severe negative impacts on human rights standards (e.g. privacy, stigmatization, discrimination), if misapplied? & & x  \\ \hline
    Does your project have the potential for terrorist or criminal abuse e.g. infrastructural vulnerability studies, cybersecurity related project? & & x  \\ \hline
    \cellcolor[HTML]{C0C0C0} SECTION 8: LEGAL ISSUES &  & \  \\ \hline
    Will your project use or produce software for which there are copyright licensing implications? & & x  \\ \hline
    Will your project use or produce goods or information for which there are data protection, or other legal implications? & & x  \\ \hline
    \cellcolor[HTML]{C0C0C0} SECTION 9: OTHER ETHICS ISSUES &  & \  \\ \hline
    Are there any other ethics issues that should be taken into consideration? & & x  \\ \hline
    \end{longtable}
\end{center}